5'CutSiteAnalysisDataGeneration

### 2023-07-24 R/5'CutSiteAnalysisDataGeneration.rmd
Add XPC and CSB 5' cut site analysis

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data")
NHF1GeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "NHF1", "general_read_sequences")
GM12878GeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "GM12878", "general_read_sequences")
DmGeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "Dm", "general_read_sequences")
arabidopsisGeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "Arabidopsis", "general_read_sequences")
yeastGeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "yeast", "general_read_sequences")
EColiGeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "E_coli_WT", "general_read_sequences")

@@

cutSiteAnalysis("CPD", "all_reps", "1h", "NHF1", NHF1GeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", humanReadMinMax, alsoComputeCombinedReadLengths = TRUE,
                alsoComputeNucFreq = TRUE, alsoCreateSequenceLogoInput = TRUE)
cutSiteAnalysis("6-4", "all_reps", "20min", "NHF1", NHF1GeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", humanReadMinMax, alsoComputeCombineReadLengths = TRUE,
                alsoCreateSequenceLogoInput = TRUE)
cutSiteAnalysis("cisplatin", "rep1", "90min", "GM12878", GM12878GeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", humanReadMinMax, alsoComputeCombinedReadLengths = TRUE,
                alsoCreateSequenceLogoInput = TRUE)
cutSiteAnalysis("CPD", "all_reps", "20min", "yeast", yeastGeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", yeastReadMinMax, alsoComputeCombinedReadLengths = TRUE,
                alsoCreateSequenceLogoInput = TRUE)
cutSiteAnalysis("CPD", "all_reps", "ZT2", "Arabidopsis", arabidopsisGeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", arabidopsisReadMinMax, alsoComputeCombinedReadLengths = TRUE,
                alsoCreateSequenceLogoInput = TRUE)
cutSiteAnalysis("CPD", "all_reps", "5min", "E_coli_WT", EColiGeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", EColiReadMinMax, alsoComputeCombinedReadLengths = TRUE,
                alsoCreateSequenceLogoInput = TRUE)
```

>>>>

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data")
NHF1GeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "NHF1", "general_read_sequences")
GM12878GeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "GM12878", "general_read_sequences")
DmGeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "Dm", "general_read_sequences")
arabidopsisGeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "Arabidopsis", "general_read_sequences")
yeastGeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "yeast", "general_read_sequences")
EColiGeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "E_coli_WT", "general_read_sequences")
CSBGeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "CS-B", "general_read_sequences")
XPCGeneralReadSequenceDataDirectory = file.path(deaminationDataDirectory, "XP-C", "general_read_sequences")

@@

cutSiteAnalysis("CPD", "all_reps", "1h", "NHF1", NHF1GeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", humanReadMinMax, alsoComputeCombinedReadLengths = TRUE,
                alsoComputeNucFreq = TRUE, alsoCreateSequenceLogoInput = TRUE)
cutSiteAnalysis("CPD", "all_reps", "1h", "CS-B", CSBGeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", humanReadMinMax, alsoComputeCombinedReadLengths = TRUE,
                alsoComputeNucFreq = TRUE, alsoCreateSequenceLogoInput = TRUE)
cutSiteAnalysis("CPD", "all_reps", "1h", "XP-C", XPCGeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", humanReadMinMax, alsoComputeCombinedReadLengths = TRUE,
                alsoComputeNucFreq = TRUE, alsoCreateSequenceLogoInput = TRUE)
cutSiteAnalysis("6-4", "all_reps", "20min", "NHF1", NHF1GeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", humanReadMinMax, alsoComputeCombineReadLengths = TRUE,
                alsoCreateSequenceLogoInput = TRUE)
cutSiteAnalysis("cisplatin", "rep1", "90min", "GM12878", GM12878GeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", humanReadMinMax, alsoComputeCombinedReadLengths = TRUE,
                alsoCreateSequenceLogoInput = TRUE)
cutSiteAnalysis("CPD", "all_reps", "20min", "yeast", yeastGeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", yeastReadMinMax, alsoComputeCombinedReadLengths = TRUE,
                alsoCreateSequenceLogoInput = TRUE)
cutSiteAnalysis("CPD", "all_reps", "ZT2", "Arabidopsis", arabidopsisGeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", arabidopsisReadMinMax, alsoComputeCombinedReadLengths = TRUE,
                alsoCreateSequenceLogoInput = TRUE)
cutSiteAnalysis("CPD", "all_reps", "5min", "E_coli_WT", EColiGeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", EColiReadMinMax, alsoComputeCombinedReadLengths = TRUE,
                alsoCreateSequenceLogoInput = TRUE)
```
